|

### 2022-12-29 paper.Rmd
autogit

```{bash ipythonRunner, include=FALSE}
# Set the base directory
EXPDIR="/Users/rmn/masterThesis/eda-gp-2020"

@@

```{python pytest, echo=FALSE}
from sys import version, executable
print(f"Python Version: {version} \nPath: {executable}")
```

@@

The DAE-GP algorithm, first described by @dae-gp_2020_rtree, is summarized by chart 1.

![DAE-GP - Flowchart](./img/flowcharts/dae-gp.png)

>>>>

```{bash compile_mermaid, include=FALSE}
# Loop through all files with the .mmd extension in the current directory

for file in ./mermaid/*.mmd
do
  # Call PROG on the current file, saving the output as a .png file
  mmdc -i "$file" -o ./img/flowcharts/$(basename "$file" .mmd).png -t light -b transparent 
done

````

```{bash ipythonRunner, eval=FALSE, include=FALSE}
# Set the base directory
EXPDIR="/Users/rmn/masterThesis/eda-gp-2020"

@@

```{python pytest, echo=FALSE, include=FALSE}
from sys import version, executable
print(f"Python Version: {version} \nPath: {executable}")
```

@@

The DAE-GP algorithm, first described by @dae-gp_2020_rtree, is summarized by figure 1.

![DAE-GP - Algorithm](./img/flowcharts/dae-gp.png)

The pre-training strategy implemented is visualized by figure 2.

![DAE-GP - Algorithm](./img/flowcharts/pt-dae-gp.png)
